Positional entropy in childes

### 2018-08-16 positional_entropy_childes.Rmd
Added bigram computations

```{r setup, include = FALSE}
# load packages
library(knitr)
library(tidyverse)
library(directlabels)
library(childesr) #data
library(SnowballC) #stemmer
library(tidytext)
library(entropy)
library(tidyboot)

@@

>>>>

```{r setup, include = FALSE}
# load packages
library(knitr)
library(tidyverse)
library(directlabels)
library(childesr) #data
library(SnowballC) #stemmer
library(tidytext)
library(entropy)
library(tidyboot)
library(dplyr)
library(tokenizers)
library(tau)

@@

new_utterances <- prov_utterances %>% filter(speaker_role=="Target_Child") %>% mutate(len = str_count(stem, " ") + 1)
#toks <- new_utterances %>%

ggplot(new_utterances, aes(x=len)) +
  geom_histogram(binwidth = 1)
```

```{r ngram_frequencies}
m_prov <- prov_utterances %>%
          filter(speaker_role == "Target_Child") %>%
          mutate(length = str_count(stem, " ") + 1) %>% 
          filter(length >= 2)

b_prov <- m_prov %>% mutate(bigrams = paste(unlist(textcnt(stem, n = 2, split = " ", method = "string")), collapse = ",")) #get all the counts of bigrams from all of the dataframe
counts <- b_prov$bigrams[1] %>% strsplit(split=',') %>% unlist() %>% as.numeric()
fileConn <- file("counts.txt")
writeLines(b_prov$bigrams[1], fileConn)
close(fileConn)

b_prov <- m_prov %>% mutate(bigrams = paste(unlist(names(textcnt(stem, n = 2, split = " ", method = "string"))), collapse = ",")) #get all of the bigrams from the entire dataframe
bigrams <- b_prov$bigrams[1] %>% strsplit(split=',') %>% unlist()
fileConn <- file("bigram_words.txt")
writeLines(b_prov$bigrams[1], fileConn)
close(fileConn)
